---
title: "Credit Risk Modelling"
author: "Ngoc Linh Dao"
date: "23 - 01 - 2024"
output: 
  html_document:
    theme: cerulean
    toc: true
    toc_float: 
      collapsed: true
      smooth_scroll: true  
    number_sections: false
---

```{r setup, include=FALSE}

options(repos = c(CRAN = "https://cloud.r-project.org/"))
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)


library(knitr)
library(stargazer)
library(pander)
library(ggplot2)
```

## 1. Credit risk modeling

```{r}

data <- read.csv("credit_data.csv")

# Convert variables
data$default <- factor(data$default, levels = c(0, 1), labels = c("false", "true")) 
data$gender <- factor(data$gender, levels = c(0, 1), labels = c("m", "f"))  #Assuming that male = 0 and female = 1
data$single <- as.numeric(data$single)  
data$owner <- as.numeric(data$owner)    
data$foreign <- as.numeric(data$foreign) 
data$job <- factor(data$job, levels = c(1, 2, 3), labels = c("little", "moderate", "high")) 
data$duration <- as.numeric(data$duration)  
data$amount <- as.numeric(data$amount)      

str(data)
```

### 1.1. Estimate different regression models (linear probability model, logit, probit) explaining the response variable default through the observed predictors.

*(a) A linear probability model of defaults*

```{r}
lpm_model <- lm(as.numeric(default) ~ gender + single + owner + foreign + job + duration + amount, data = data)
summary(lpm_model)
```

**Brief evaluation of the model**

1.  **R-squared and adjusted R-squared**: The R-squared value indicates the proportion of variance in the response variable that is explained by the predictors in the model. In this case, the R-squared value is quite low (0.0577), indicating that the model explains only a small portion (5.77%) of the variance in the response variable. After adjusting for the number of predictors, the explanatory power remains low (5.01%).

2.  **F-statistic**: The F-statistic tests the overall significance of the model. Here, it is significant, indicating that at least one of the predictors is related to the response variable.

Based on the evaluation, the model seems to have some predictive power, but its overall explanatory ability is limited (low R-squared and adjusted R-squared). Additionally, some predictor variables may not be contributing significantly to the model.

*(b) A logit model*

```{r}
logit_model <- glm(default ~ gender + single + owner + foreign + job + duration + amount, 
                   data = data, family = binomial(link = "logit"))
summary (logit_model)
```

*(c) A probit model*

```{r}
probit_model <- glm(default ~ gender + single + owner + foreign + job + duration + amount, 
                   data = data, family = binomial(link = "probit"))
summary (probit_model)
```

In comparison to the logit model, the probit model substitutes the cumulative distribution function of the logistic distribution for the standard normal distribution as its "link" function.

$$G(z) = Φ(z)$$

with

$$Φ(z)=P(Z≤z) , Z∼N(0,1),$$

The rest of the structure stays pretty much the same.

### 1.2. Compare the models via AIC and BIC.

First, we extract AIC and BIC from the 3 models:

-   AIC:

    ```{r}
    AIC (lpm_model)
    AIC (logit_model)
    AIC (probit_model)
    ```

-   BIC:

    ```{r}
    BIC (lpm_model)
    BIC (logit_model)
    BIC (probit_model)
    ```

| Models/Criteria          | AIC      | BIC      |
|--------------------------|----------|----------|
| Linear probability model | 1237.798 | 1286.875 |
| Logit model              | 1180.729 | 1224.899 |
| Probit model             | 1180.446 | 1224.616 |

**Comparison:**

Lower AIC and BIC values indicate a better model fit relative to other models.

In terms of AIC, the probit model has the lowest value, followed by the logit model, and the linear probability model has the highest value. This suggests that the probit model might be the best model among the three according to the AIC criterion.

In terms of BIC, again, the probit model has the lowest value, followed by the logit model, and the linear probability model has the highest value. This also suggests that the probit model might be the best model among the three according to the BIC criterion.

Although the BIC works similarly to the AIC, where lower values mean the model fits better, they have different motivations: the BIC penalizes complex models much more than the AIC. Since the three models share the same set of variables, the BIC of the logit and probit models are quite similar, yet, the probit model still obtained a slightly better result, indicating the probit model is the best fit for the regression.

### 1.3. Which predictors are statistically significant? Interpret the estimated coefficients

***(a) Linear probability model***

+-------------------------------+-----------+----------+--------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Variable                      | Estimate  | p-value  | Significance       | Interpretation                                                                                                                                                                                                                        |
+===============================+===========+==========+====================+=======================================================================================================================================================================================================================================+
| Intercept                     | 1.30725   | \<2e-16  | Highly significant | The predicted probability of default for the reference group (female, not single, not homeowner, native, little education) is 1.307.                                                                                                  |
|                               |           |          |                    |                                                                                                                                                                                                                                       |
|                               |           |          |                    | This is invalid, as probabilities must be between [0,1]. This highlights a major flaw of the LPM.                                                                                                                                     |
+-------------------------------+-----------+----------+--------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| gender                        | 0.006692  | 0.883345 | Not significant    | Being female increases the probability of default by 0.67 percentage points, but this effect is not statistically significant                                                                                                         |
+-------------------------------+-----------+----------+--------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| single                        | -0.065779 | 0.124447 | Not significant    | Being single decreases the probability of default by 6.58 percentage points, but this effect is not statistically significant.                                                                                                        |
+-------------------------------+-----------+----------+--------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| home owner                    | -0.109645 | 0.000584 | Highly significant | Being a homeowner reduces the probability of default by 10.96 percentage points (statistically significant). If a person switches from not owning to owning a home, their probability of default decreases by \~11 percentage points. |
+-------------------------------+-----------+----------+--------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| foreign                       | 0.172300  | 0.022180 | Significant        | Being a foreign citizen increases the probability of default by 17.23 percentage points.                                                                                                                                              |
+-------------------------------+-----------+----------+--------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| job (from little to moderate) | -0.028101 | 0.772723 | Not significant    | Having moderate education (compared to little education) reduces the probability of default by 2.81 percentage points, but this effect is not statistically significant.                                                              |
+-------------------------------+-----------+----------+--------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| job (from little to high)     | -0.032995 | 0.750208 | Not significant    | Having high education (compared to little education) reduces the probability of default by 3.3 percentage points, but this effect is not statistically significant.                                                                   |
+-------------------------------+-----------+----------+--------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| duration                      | -0.003226 | 0.012169 | Significant        | For each additional month of mortgage duration, the probability of default decreases by 0.32 percentage points                                                                                                                        |
+-------------------------------+-----------+----------+--------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| amount                        | 0.050051  | 3.73e-06 | Highly significant | For each additional €1,000 in mortgage amount, the probability of default increases by 5.01 percentage points.                                                                                                                        |
+-------------------------------+-----------+----------+--------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

***(b) Logit model:***

Beside the coefficients themselves, we can also observe the change in the odds ratio by using the exponential function as follows:

$$\frac{P(Y=1|X=x)}{1-P(Y=1|X=x)} = e^{\beta_0} * e^{\beta_1X_1}$$ $$\frac{P(Y=1|X=x+1)}{1-P(Y=1|X=x+1)} = e^{\beta_0} * e^{\beta_1(X_1+1)}$$ $$odd(x+1) = e^{\beta_0} * e^{\beta_1X_1} * e^{\beta_1} = odd(x)*e^{\beta_1}$$ Utimately:

$$\frac{odd(x+1)}{odd(x)} = e^{\beta_1}$$

```{r}
exp(coefficients(logit_model))
```

The coefficients could also be transformed into probability using:

```{r}
plogis(coefficients(logit_model))
```

+-------------------------------+-----------+----------------+----------+--------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Variable                      | Estimate  | Change in odds | p-value  | Significance       | Interpretation                                                                                                                                                                                                                          |
+===============================+===========+================+==========+====================+=========================================================================================================================================================================================================================================+
| Intercept                     | -1.230244 | 0.2922213      | 0.117    | Not significant    | The coefficient for the intercept is estimated at -1.230244, meaning that when all predictor variables are zero, the log of the odds ratio of default is expected to be -1.23, ceteris paribus.                                         |
|                               |           |                |          |                    |                                                                                                                                                                                                                                         |
|                               |           |                |          |                    | Converting this to odds: exp(-1.230244) = 0.2920                                                                                                                                                                                        |
|                               |           |                |          |                    |                                                                                                                                                                                                                                         |
|                               |           |                |          |                    | This means that when all predictors are at their reference levels (baseline case), the odds of default are 0.292, or a 22.6% probability of default.                                                                                    |
|                               |           |                |          |                    |                                                                                                                                                                                                                                         |
|                               |           |                |          |                    | (However, this effect is not statistically significant, p = 0.117.)                                                                                                                                                                     |
+-------------------------------+-----------+----------------+----------+--------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| genderf                       | 0.018424  | 1.0185947      | 0.934    | Not significant    | The coefficient for gender (female) is estimated at 0.018424, indicating that being female increases the log of odds ratio of default by 0.018, ceteris paribus.\                                                                       |
|                               |           |                |          |                    | As exp(0.018424) = 1.0186, this means that being female increases the odds of default by only 1.86%, ceteris paribus.\                                                                                                                  |
|                               |           |                |          |                    | *(However, this effect is not statistically significant, as p = 0.934.)*                                                                                                                                                                |
+-------------------------------+-----------+----------------+----------+--------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| single                        | -0.339122 | 0.7123956      | 0.112    | Not significant    | The coefficient for single is estimated at -0.339122, indicating that being single reduces the log of odds ratio of default by 0.339, ceteris paribus.\                                                                                 |
|                               |           |                |          |                    | As exp(-0.339122) = 0.7124, this means that being single reduces the odds of default by 28.8% compared to non-single households, ceteris paribus.\                                                                                      |
|                               |           |                |          |                    | *(However, this effect is not statistically significant, as p = 0.112.)*                                                                                                                                                                |
+-------------------------------+-----------+----------------+----------+--------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| home owner                    | -0.519006 | 0.5951119      | 0.0007   | Highly significant | The coefficient for owner is estimated at -0.519006, indicating that homeowners have a lower log-odds ratio of default by 0.519, compared to non-homeowners, ceteris paribus.\                                                          |
|                               |           |                |          |                    | As exp(-0.519006) = 0.5950, this means that homeowners have 40.5% lower odds of defaulting compared to non-homeowners, ceteris paribus.                                                                                                 |
+-------------------------------+-----------+----------------+----------+--------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| foreign                       | 1.248603  | 3.4854696      | 0.0226   | Significant        | The coefficient for foreign is estimated at 1.248603, indicating that being a foreigner increases the log of odds ratio of default by 1.2486, ceteris paribus.\                                                                         |
|                               |           |                |          |                    | As exp(1.248603) = 3.4844, this means that foreigners have 3.48 times higher odds of defaulting compared to natives, ceteris paribus.                                                                                                   |
+-------------------------------+-----------+----------------+----------+--------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| job (from little to moderate) | -0.104043 | 0.9011869      | 0.832    | Not significant    | The coefficient for jobmoderate is estimated at -0.104043, meaning that having a moderate-level job decreases the log of odds ratio of default by 0.104, ceteris paribus.\                                                              |
|                               |           |                |          |                    | As exp(-0.104043) = 0.9011, this means that individuals with moderate jobs have 9.89% lower odds of defaulting, ceteris paribus. *(Not significant, p = 0.832.)*                                                                        |
+-------------------------------+-----------+----------------+----------+--------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| job (from little to high)     | -0.114241 | 0.8920427      | 0.826    | Not significant    | The coefficient for jobhigh is estimated at -0.114241, meaning that having a high-level job decreases the log of odds ratio of default by 0.114, ceteris paribus.\                                                                      |
|                               |           |                |          |                    | As exp(-0.114241) = 0.8920, this means that individuals with high-level jobs have 10.8% lower odds of defaulting, ceteris paribus. *(Not significant, p = 0.827.)*                                                                      |
+-------------------------------+-----------+----------------+----------+--------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| duration                      | -0.017025 | 0.9831192      | 0.0113   | Significant        | The coefficient for duration is estimated at -0.017025, indicating that when the mortgage duration increases by one month, the log of odds ratio of default is expected to decrease by 0.017, ceteris paribus.\                         |
|                               |           |                |          |                    | As exp(-0.017025) = 0.9831, this means that when the mortgage duration increases by one month, the odds of default will decrease by 1.7%, ceteris paribus.                                                                              |
+-------------------------------+-----------+----------------+----------+--------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| amount                        | 0.232915  | 1.2622742      | 5.88e-06 | Highly significant | The coefficient for this variable is estimated at 0.232915, indicating that when the mortgage amount increase by one unit (equivalent to 1000 euro), the log of odds ratio of default is expected to increase by 0.23, ceteris paribus. |
|                               |           |                |          |                    |                                                                                                                                                                                                                                         |
|                               |           |                |          |                    | As exp(0.23)=1.2622742, meaning when the mortgage amount increase by one unit (equivalent to 1000 euro), the odds of default will increase by 26%, ceteris paribus.                                                                     |
+-------------------------------+-----------+----------------+----------+--------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

***(c) The probit model***

-   Since the probit model uses the cumulative standard normal distribution function $Φ(z)$, the coefficients acquired from the regression can be transformed back into probability using pnorm function

```{r}
 pnorm(coefficients(probit_model))
```

+-------------------------------+-----------+----------------+----------+--------------------+----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Variable                      | Estimate  | Change in odds | p-value  | Significance       | Interpretation                                                                                                                                                                                                 |
+===============================+===========+================+==========+====================+================================================================================================================================================================================================================+
| Intercept                     | -0.740792 | 0.2294098      | 0.097828 | Not significant    | The coefficient for the intercept is estimated at -0.740792, meaning that when all predictor variables are zero, the probit (inverse standard normal) of the probability of default is -0.74, ceteris paribus. |
|                               |           |                |          |                    |                                                                                                                                                                                                                |
|                               |           |                |          |                    | This corresponds to a baseline probability of default: 0.2290. This means that when all predictors are at their reference levels, the probability of default is 22.9%.                                         |
|                               |           |                |          |                    |                                                                                                                                                                                                                |
|                               |           |                |          |                    | (However, this effect is not statistically significant, p = 0.117.)                                                                                                                                            |
+-------------------------------+-----------+----------------+----------+--------------------+----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| genderf                       | 0.008290  | 0.5033072      | 0.950956 | Not significant    | The coefficient for gender (female) is estimated at 0.008290, indicating that being female increases the probit of the probability of default by 0.0083, ceteris paribus.                                      |
|                               |           |                |          |                    |                                                                                                                                                                                                                |
|                               |           |                |          |                    | As Φ(0.008290)=0.5033, this means that being female has no meaningful impact on the probability of default, ceteris paribus.                                                                                   |
+-------------------------------+-----------+----------------+----------+--------------------+----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| single                        | -0.204559 | 0.4189583      | 0.110380 | Not significant    | The coefficient for single is estimated at -0.204559, indicating that being single reduces the z-score of default by 0.2046, ceteris paribus.                                                                  |
|                               |           |                |          |                    |                                                                                                                                                                                                                |
|                               |           |                |          |                    | As Φ(−0.204559)=0.4190, this means that single individuals are less likely to default ( approximately 41.9%), ceteris paribus.                                                                                 |
+-------------------------------+-----------+----------------+----------+--------------------+----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| home owner                    | -0.316354 | 0.3758671      | 0.000683 | Highly significant | The coefficient for owner is estimated at -0.316354, indicating that homeowners have a lower z-score by 0.316, compared to non-homeowners, ceteris paribus.                                                    |
|                               |           |                |          |                    |                                                                                                                                                                                                                |
|                               |           |                |          |                    | As Φ(−0.316354)=0.3767, this means that homeowners have significantly lower probability of defaulting (approximately 37.7%), ceteris paribus.                                                                  |
+-------------------------------+-----------+----------------+----------+--------------------+----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| foreign                       | 0.738905  | 0.7700177      | 0.011780 | Significant        | The coefficient for foreign is estimated at 0.738905, indicating that being a foreigner increases z-score by 0.7389, ceteris paribus.                                                                          |
|                               |           |                |          |                    |                                                                                                                                                                                                                |
|                               |           |                |          |                    | As Φ(0.738905)=0.7691, this means that foreigners have a significantly higher probability of defaulting (approximately 76.9%), ceteris paribus.                                                                |
+-------------------------------+-----------+----------------+----------+--------------------+----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| job (from little to moderate) | -0.057860 | 0.4769300      | 0.844942 | Not significant    | The coefficient for jobmoderate is estimated at -0.057860, meaning that having a moderate-level job decreases the z-score by 0.058, ceteris paribus.                                                           |
|                               |           |                |          |                    |                                                                                                                                                                                                                |
|                               |           |                |          |                    | As Φ(−0.057860)=0.4769, this means that individuals with moderate-level jobs have slightly lower probability of default (approximately 47.7%), ceteris paribus.                                                |
+-------------------------------+-----------+----------------+----------+--------------------+----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| job (from little to high)     | -0.055063 | 0.4780440      | 0.860762 | Not significant    | The coefficient for jobhigh is estimated at -0.055063, meaning that having a high-level job decreases the z-score by 0.055, ceteris paribus.                                                                   |
|                               |           |                |          |                    |                                                                                                                                                                                                                |
|                               |           |                |          |                    | As Φ(−0.055063)=0.4781, this means that individuals with high-level jobs have slightly lower probability of default (approximately 47.8%), ceteris paribus.                                                    |
+-------------------------------+-----------+----------------+----------+--------------------+----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| duration                      | -0.010192 | 0.4959340      | 0.010225 | Significant        | The coefficient for duration is estimated at -0.010192, indicating that when the mortgage duration increases by one month, z-score is expected to decrease by 0.0102, ceteris paribus.                         |
|                               |           |                |          |                    |                                                                                                                                                                                                                |
|                               |           |                |          |                    | As Φ(−0.010192)=0.9899, this means that when the mortgage duration increases by one month, the probability of default decrease by approximately 1.01%, ceteris paribus.                                        |
+-------------------------------+-----------+----------------+----------+--------------------+----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| amount                        | 0.140415  | 0.5558338      | 7.48e-06 | Highly significant | The coefficient for amount is estimated at 0.140415, indicating that when the mortgage amount increases by one unit (equivalent to 1000 euros), the z-score is expected to increase by 0.140, ceteris paribus. |
|                               |           |                |          |                    |                                                                                                                                                                                                                |
|                               |           |                |          |                    | As Φ(0.140415)=1.151, this means that when the mortgage amount increases by 1000 euros, the probability of default increase by approximately 15.1%, ceteris paribus.                                           |
+-------------------------------+-----------+----------------+----------+--------------------+----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

### 1.4. Use the different models to predict the default probability for a highly qualified female foreigner who is single and does not own a home, for a mortgage of 3000 euros over a duration of 18 months

```{r}
new_data <- data.frame(amount = 3, gender = "f", single = 1, owner = 0, foreign = 1,  job = "high", duration = 18)
```

**(a) Using the LPM:**

```{r}
predict_lpm <- predict(lpm_model, newdata = new_data, type = "response")
print(paste("the default risk of the subject of interest, according to the LPM, is", format(round(predict_lpm*100, digits = 2), nsmall = 2),"%"))
```

This is not really feasible in terms of probability. This could be due to the fact that the dependent variable "default" is perceived as factor(true, false). We can try to predict using a LPM where "default" takes the value from 0 to 1 (0= no default, 1 = default)

```{r}
data$default1 <- as.numeric(data$default) - 1

lpm_model1 <- lm(default1 ~ gender + single + owner + foreign + job + duration + amount, data = data)
summary(lpm_model1)
```

With the intercept looking more reasonable, we can try to predict the value again:

```{r}
predict_lpm <- predict(lpm_model1, newdata = new_data, type = "response")
print(paste("the default risk of the subject of interest, according to the LPM, is", format(round(predict_lpm*100, digits = 2), nsmall = 2),"%"))
```

**(b) Using the logit model:**

```{r}
predict_logit <- predict(logit_model, newdata = new_data, type = "response")
print(paste("the default risk of the subject of interest, according to the Logit model, is", format(round((predict_logit)*100, digits = 2), nsmall = 2),"%"))
```

**(c) Using the probit model:**

```{r}
predict_probit <- predict(probit_model, newdata = new_data, type = "response")
print(paste("the default risk of the subject of interest, according to the Probit model, is", format(round((predict_probit)*100, digits = 2), nsmall = 2),"%"))
```

### 1.5. How does the risk change if the person owns her own home?

```{r}
predict_data_2 <- data.frame(amount = 3, gender = "f", single = 1, owner = 1, foreign = 1,  job = "high", duration = 18)
```

**(a) Using the LPM:**

```{r}
predict_lpm_2 <- predict(lpm_model, newdata = predict_data_2, type = "response")
print(paste("the default risk of the subject of interest, according to the LPM, is", format(round(predict_lpm_2*100, digits = 2), nsmall = 2),"%"))
```

Again, let's try to use the LPM where "default" takes the value from 0 to 1 (0= no default, 1 = default):

```{r}
predict_lpm_2 <- predict(lpm_model1, newdata = predict_data_2, type = "response")
print(paste("the default risk of the subject of interest, according to the LPM, is", format(round(predict_lpm_2*100, digits = 2), nsmall = 2),"%"))
```

**(b) Using the logit model:**

```{r}
predict_logit_2 <- predict(logit_model, newdata = predict_data_2, type = "response")
print(paste("the default risk of the subject of interest, according to the Logit model, is", format(round((predict_logit_2)*100, digits = 2), nsmall = 2),"%"))
```

**(c) Using the probit model:**

```{r}
predict_probit <- predict(probit_model, newdata = predict_data_2, type = "response")
print(paste("the default risk of the subject of interest, according to the Probit model, is", format(round((predict_probit)*100, digits = 2), nsmall = 2),"%"))
```

+------------------+---------------+-----------+---------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Model/Covariates | Not homeowner | Homeowner | Changes in risk                                                                                                                                               |
+==================+===============+===========+===============================================================================================================================================================+
| LPM              | 47.96 %       | 36.99 %   | -10.97 %                                                                                                                                                      |
+------------------+---------------+-----------+---------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Logit model      | 49.39 %       | 36.74 %   | -12.65 % (odds of default when is a homeowner is 40.2% lower than is not a homeowner, quite similar to what was given by the coefficients of the logit model) |
+------------------+---------------+-----------+---------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Probit model     | 49.38 %       | 37.00 %   | -12.38 %                                                                                                                                                      |
+------------------+---------------+-----------+---------------------------------------------------------------------------------------------------------------------------------------------------------------+
